---
title: "diffdf tour"
author: "kieran martin"
date: "19 September 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We are going to explore some of diffdf's capabilities. We're going to use a package called salty to add some realistic errors, to see how they look when using diffdf

```{r cars}
library(diffdf)
library(dplyr)
library(salty)


```

```{r, include=FALSE}

LENGTH = 30
set.seed(12334)
test_data <- tibble::tibble( 
    ID          = 1:LENGTH,
    GROUP1      = rep( c(1,2) , each = LENGTH/2),
    GROUP2      = rep( c(1:(LENGTH/2)), 2 ),
    INTEGER     = rpois(LENGTH , 40),
    BINARY      = sample( c("M" , "F") , LENGTH , replace = T),
    DATE        = lubridate::ymd("2000-01-01") + rnorm(LENGTH, 0, 7000),
    DATETIME    = lubridate::ymd_hms("2000-01-01 00:00:00") + rnorm(LENGTH, 0, 200000000), 
    CONTINUOUS  = rnorm(LENGTH , 30 , 12),
    CATEGORICAL = factor(sample( c("A" , "B" , "C") , LENGTH , replace = T)),
    LOGICAL     = sample( c(TRUE , FALSE) , LENGTH , replace = T),
    CHARACTER   = stringi::stri_rand_strings(LENGTH,  rpois(LENGTH , 13),  pattern = "[ A-Za-z0-9]")
)
```

We are going to work with some dummy data with lots of different data types

```{r}
test_data

```
Lets begin by seeing what happens if we alter the class of our data

```{r}
test_data2 <- test_data
class(test_data2$GROUP1) <- "different"
class(test_data2$BINARY) <- "another difference"
diffdf(test_data, test_data2)
```

Lets's try fiddling with the columns next

```{r}
test_data2 <- test_data
test_data2$GROUP1 <- NULL
test_data2$newcol <- 5

diffdf(test_data, test_data2)
```

For row by row comparison, it's usually best to specify a key on which to compare datasets

```{r}
test_data2 <- test_data[7:28,]

diffdf(test_data, test_data2, keys = "ID")
```

Now let's look at modifying values. Here we will make use of some "salty" functions to modify the data

```{r}
test_data2 <- test_data
test_data2 <- test_data2 %>% 
  mutate_if(is.character, salt_insert, insertions = shaker$mixed_letters) 
diffdf(test_data, test_data2, keys = "ID")
```
We don't have to rely on the print method, we can instead save the object and interrogate it:

```{r}

save <- diffdf(test_data, test_data2, keys = "ID")
save$VarDiff_BINARY

```

Doing this also allows us to make use of another diffdf function, `diffdf_issuerows()`

```{r}
diffdf_issuerows(test_data, save)
```


