---
title: "Diffdf"
author: "Craig Gower and Kieran Martin"
date: "2018/08/16"
output:
  xaringan::moon_reader:
    css: ["./libs/remark-css/default.css","./libs/remark-css/metropolis.css", "./libs/remark-css/metropolis-fonts.css" ]
    lib_dir: libs
    chakra:  libs/remark-latest.min.js
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# Outline
.font150[
Who are we?

What was the problem?

How does diffdf solve it?

Our future plans for the package
]

---

# Who are we?


.content-box-green[
Kieran Martin and Craig Gower
]
--
<br>
.content-box-blue[
Both members of I2ON SPA-DA group  at Roche
]
--
<br>
.content-box-green[
Both advocates for R usage within SPA and across the organisation
]

  


---

# What was the problem?

One key piece of programming work is setting up and qcing analysis datasets

We believe this can be done in R
--
.content-box-green[
How do we compare qc datasets?
]

---

# With diffdf!

**diffdf**
.content-box-green[
Package for **comparing datasets**

Gives **informative feedback** on where issues are
]

--

Main page: https://gowerc.github.io/diffdf/

Now on CRAN: https://CRAN.R-project.org/package=diffdf

Check out github: https://github.com/gowerc/diffdf

---
# diffdf tour of capabilities

<a href = "diffdftour.html">Tour of capabilities</a>

---

# diffdf: missing columns:
<br>

```{r, include = FALSE}

LENGTH = 30
set.seed(12334)
test_data <- tibble::tibble( 
    ID          = 1:LENGTH,
    GROUP1      = rep( c(1,2) , each = LENGTH/2),
    GROUP2      = rep( c(1:(LENGTH/2)), 2 ),
    INTEGER     = rpois(LENGTH , 40),
    BINARY      = sample( c("M" , "F") , LENGTH , replace = T),
    DATE        = lubridate::ymd("2000-01-01") + rnorm(LENGTH, 0, 7000),
    DATETIME    = lubridate::ymd_hms("2000-01-01 00:00:00") + rnorm(LENGTH, 0, 200000000), 
    CONTINUOUS  = rnorm(LENGTH , 30 , 12),
    CATEGORICAL = factor(sample( c("A" , "B" , "C") , LENGTH , replace = T)),
    LOGICAL     = sample( c(TRUE , FALSE) , LENGTH , replace = T),
    CHARACTER   = stringi::stri_rand_strings(LENGTH,  rpois(LENGTH , 13),  pattern = "[ A-Za-z0-9]")
)
```


```{r, warning=FALSE}
library(diffdf)

test_data2 <- test_data 
test_data2 <- test_data2[,-6]
diffdf(test_data , test_data2)
```
---
# diffdf: missing rows
<br>
```{r, warning=FALSE}
test_data2 <- test_data
test_data2 <- test_data2[1:(nrow(test_data2) - 2),]
diffdf(test_data, test_data2, keys = "ID")
```
---
# diffdf: different values
<br>
```{r, warning=FALSE}
test_data2 <- test_data
test_data2[5,2] <- 6
difval <- diffdf(test_data , test_data2, keys = "ID" )
difval$NumDiff
difval$VarDiff_GROUP1
```
---
# diffdf: different attributes
<br>
```{r, warning=FALSE}
test_data2 <- test_data
attr(test_data$ID , "label") <- "This is a interesting label"
attr(test_data2$ID , "label") <- "A different label"
diffdf(test_data , test_data2, keys = "ID" )
```
---

# Future plans for diffdf

.content-box-green[
Make it even faster with optimisation
]
--
<br>
.content-box-blue[
Adding html views of the comparisons
]
--
<br>
.content-box-green[
Refining based on feedback
]

# Any questions?




